Efficient Coalition Formation \\ for Web Services

### 2013-06-02 papers/coalition-journal-extension/coalition_journal.tex
Changes

In the first example, we present a community with $R_C$ value of 10, and three web services each having different $QoS_{ws}$ and $Th_{ws}$ values as listed in table \ref{example_1}.

>>>>

We present an example with a community with $R_C$ value of 10, and three web services each having different $QoS_{ws}$ and $Th_{ws}$ values as listed in table \ref{example_1}.
